Improving Software Maintainability through Automated Refactoring of Code Clones

### 2020-04-26 ase/paper.tex
Updates from Overleaf

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. Several studies show however, that not all duplication should be refactored. When some duplication is refactored, other system attributes are negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered. % To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability. Moreover, manual code clone refactoring is often tedious and could benefit from an automated tool.

We use software maintainabilty metrics to determine the impact of refactoring 
We consider the ``duplicate code'' code smell from a maintainability perspective. We analyze 
%We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them using the ``Extract Method'' refactoring technique. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open-source Java projects.

We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings. We find that the biggest influencing factor is the size of the clone. The majority of duplicates with 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the extracted method is the other important factor: the majority of extracted methods requiring more than two parameters decrease maintainability.
\end{abstract}

@@

>>>>

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. Several studies show however, that not all duplication should be refactored. When some duplication is refactored, other system attributes are negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered.
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate several maintainability metrics (duplication, complexity, unit size, code volume) to determine whether it improves the code. To simulate such refactorings in a controlled environment, we propose a tool that can automatically refactor a subset of duplication problems in Java source code. Our tool refactors 13k clones over 2k open source Java projects and measures the delta maintainability scores of the refactoring.

We correlate the delta maintainability score with the factors that influence this score (clone volume, clone complexity, externally declared data used). We find that the biggest influencing factor is the volume of the clone. Our data shows that clones consisting of 63 or fewer tokens most often shouldn't be refactored. The other important factor is externally declared data that is used in the clone, clones with more than two externally declared variables most often do not improve maintainability when refactored.
\end{abstract}

@@

\section{Threats to validity}
This research relies on the assumption that the maintainability model proposed by Heitlager et al.~\cite{heitlager2007practical} gives a good indication of the actual maintainabilty of a system. Furthermore, we rely on that the scores of different metrics have an equal weight relative to each other, as for our aggregation of the scores.
